\texorpdfstring{\ZpL}{ZpL}: a p-adic precision package

### 2018-05-08 ZpL/ZpL.tex
copyright
ACM info after \begin{document}

\documentclass[sigconf]{acmart}

@@

\newtheorem{theo}{Theorem}[section]
\newtheorem{lem}[theo]{Lemma}
\newtheorem{prop}[theo]{Proposition}
\newtheorem{cor}[theo]{Corollary}
\newtheorem{quest}[theo]{Question}
\newtheorem{conj}[theo]{Conjecture}
\theoremstyle{definition}
\newtheorem{rmk}[theo]{Remark}
\newtheorem{ex}[theo]{Example}
\newtheorem{deftn}[theo]{Definition}
\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmlicensed}
\acmConference[ISSAC'18]{2018 ACM International Symposium on Symbolic and Algebraic Computation}{July 16--19, 2018}{New York, NY, USA}
\acmBooktitle{ISSAC'18: 2018 ACM Int'l Symposium on Symbolic \& Algebraic Computation, July 16--19, 2018, NY, NY, USA}
\acmPrice{15.00}
\acmDOI{10.1145/XXXXXX.XXXXXX}
\acmISBN{978-1-4503-5550-6/18/07}

@@

@@

\author{Xavier Caruso}
  \affiliation{Universit\'e Rennes 1; \\
  %\institution{IRMAR}
  %\city{Rennes, France}
  %\postcode{35042}
}
\email{xavier.caruso@normalesup.org}
\author{David Roe}
  \affiliation{MIT; \\
  %\institution{Department of Mathematics}
  %\city{Cambridge, MA, USA}
  %\postcode{02139}
}
\email{roed@mit.edu}
\author{Tristan Vaccon}
  \affiliation{Universit\'e de Limoges; \\
  %\institution{CNRS, XLIM UMR 7252}
  %\city{Limoges, France}  
  %\postcode{87060}  
  }
\email{tristan.vaccon@unilim.fr}

@@

In \S \ref{sec:implementation} we give more details on the implementation.
\S \ref{ssec:preclemma} contains a brief overview on the theory of
$p$-adic precision of \cite{caruso-roe-vaccon:14a}. 
In the next two subsections, we explain in more details how our package
works. \S \ref{ssec:trackprec} is devoted to the implementation of 
automatic differentiation leading to the actual computation of the
module that models the precision.
In \S \ref{ssec:viewprec}, we explain how precision on any individual number
can be recovered and discuss the validity
of our results.
The complexity overhead induced by our package is analyzed in
\S \ref{ssec:complexity}.

Finally, \S \ref{sec:conclusion} contains a discussion of how we see this
package fitting into the existing $p$-adic implementations.  While these
methods do introduce overhead, they are well suited to exploring
precision behavior when designing algorithms, and can provide
hints as to when further precision analysis would be useful.

>>>>

\documentclass[sigconf]{acmart}
%\documentclass{acmart}

@@

\newtheorem{theo}{Theorem}[section]
\newtheorem{lem}[theo]{Lemma}
\newtheorem{prop}[theo]{Proposition}
\newtheorem{cor}[theo]{Corollary}
\newtheorem{quest}[theo]{Question}
\newtheorem{conj}[theo]{Conjecture}
\theoremstyle{definition}
\newtheorem{rmk}[theo]{Remark}
\newtheorem{ex}[theo]{Example}
\newtheorem{deftn}[theo]{Definition}

@@

\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmlicensed}
\acmConference[ISSAC '18]{2018 ACM International Symposium on Symbolic and
Algebraic Computation}{July 16--19, 2018}{New York, NY, USA}
\acmBooktitle{ISSAC '18: 2018 ACM International Symposium on Symbolic and
Algebraic Computation, July 16--19, 2018, New York, NY, USA}
\acmPrice{15.00}
\acmDOI{10.1145/3208976.3208995}
\acmISBN{978-1-4503-5550-6/18/07}

%\CopyrightYear{2018}
%\setcopyright{acmlicensed}
%\conferenceinfo{ISSAC '18,}{July 16--19, 2018, New York, NY, USA}
%\isbn{978-1-4503-5550-6/18/07}\acmPrice{$15.00}
%\doi{https://doi.org/10.1145/3208976.3208995}

@@

\author{Xavier Caruso}
  \affiliation{CNRS, Universit\'e Rennes 1; \\
  %\institution{IRMAR}
  %\city{Rennes, France}
  %\postcode{35042}
}
\email{xavier.caruso@normalesup.org}
\author{David Roe}
  \affiliation{MIT; \\
  %\institution{Department of Mathematics}
  %\city{Cambridge, MA, USA}
  %\postcode{02139}
}
\email{roed@mit.edu}
\author{Tristan Vaccon}
  \affiliation{Universit\'e de Limoges; \\
  %\institution{CNRS, XLIM UMR 7252}
  %\city{Limoges, France}  
  %\postcode{87060}  
  }
\email{tristan.vaccon@unilim.fr}

@@

In \S \ref{sec:implementation} we give more details on the implementation.
\S \ref{ssec:preclemma} contains a brief overview on the theory of
$p$-adic precision of \cite{caruso-roe-vaccon:14a}. 
In the next two subsections, we explain in more details how our package
works. \S \ref{ssec:trackprec} is devoted to the implementation of 
automatic differentiation leading to the actual computation of the
module that models the precision.
In \S \ref{ssec:viewprec}, we explain how precision on any individual number
can be recovered and discuss the validity
of our results.
The complexity overhead induced by our package is analyzed in
\S \ref{ssec:complexity}.
Finally, \S \ref{sec:conclusion} contains a discussion of how we see this
package fitting into the existing $p$-adic implementations.  While these
methods do introduce overhead, they are well suited to exploring
precision behavior when designing algorithms, and can provide
hints as to when further precision analysis would be useful.
